### 2014-08-11 nips_rebuttal_1262.txt

Summaries (scores)
------------------
Assigned_Reviewer_15 (5): This paper is an extension of the R-CNN window proposal-based object detection algorithm of Girshick et al.'CVPR 2014. The novelty of the paper is limited but it has an interesting idea of using the output of the intermediate layers in the CNN hierarchy. The experiments are solid and demonstrate speeding-up R-CNN, at only a reasonable loss in performance. However, most of the speedup can be obtained by training a foreground-background classifier on the window proposals and processing the highest-scoring ones. The paper lacks details at multiple places needed to reproduce the results. The significance beyond the specific set-up of Girshick et al.'14 is not clear.

Assigned_Reviewer_43 (4): This paper presents several approaches to speed up the Region-based CNN. The approaches are rather heuristic and the novelty is limited. The experimental evaluations are not adequate either.

Assigned_Reviewer_9 (7): Speeding up the very slow but state-of-the-art R-CNN algorithm is of practical consequence for computer vision and the current paper offers a comprehensive and well-performing solution using a collection of suitable approaches. The paper is generally well written and experimental results are convincing.

Rebuttal
--------
We thank the reviewers for their thoughtful consideration.
We feel that the impact of our novel Cascaded CNN model was underestimated.
If given the chance, we will build a clear rhetorical focus on this contribution.
Our proposed method is conceptually distinct and orthogonal to the most recent speedups of such architectures reported, even after time of submission.

### 2014-12-15 abstract.tex
minor changes
integrating changes from thesis

%!TEX root=paper.tex
\begin{abstract}
The recently introduced R-CNN object detection framework has excellent detection accuracy, but is slow, running at 10 seconds per image on a GPU.
R-CNN is slow because it classifies roughly 2k regions of interest (ROIs) per image without sharing computation between them.
We propose and evaluate two novel speed-ups for R-CNN.
First, we re-order regions to process the most promising ones first using one of three ``fast features'': (1) region overlap statistics; (2) CNN pixel gradient statistics; and (3) the \emph{Pyramid R-CNN}, which approximates R-CNN by using a feature pyramid to share computation.
Second, we propose a novel \emph{Cascaded CNN} that adds a \emph{reject} option after each CNN layer, which yields fast but accurate classification.
We achieve a 8x speed-up while losing no more than 10\% of the top R-CNN detection performance -- or a 16x speed-up while losing no more than 20\%.
\end{abstract}

>>>>

%!TEX root=paper.tex
\begin{abstract}
We propose methods for speeding up CNN-based detection approaches while maintaining their high accuracy: (1) a dynamic region selection method using novel quick-to-compute features; and (2) the Cascade CNN, which adds a reject option between expensive convolutional layers and allows the network to terminate some computation early.
The Cascade CNN is applicable to most class-imbalanced prediction tasks.
We evaluate our approach with respect to the R-CNN object detection system, and achieve a 8x speed-up while losing no more than 10\% of the top R-CNN detection performance -- or a 16x speed-up while losing no more than 20\%.
\end{abstract}

### 2014-12-15 ccnn_fig.tex
integrating changes from thesis

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/ccnn.pdf}
\caption{
The Cascaded CNN has a reject option after pool1, pool2 and conv3 layers.
}\label{fig:ccnn}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/ccnn-expanded.pdf}
\caption{
The Cascade CNN has a Reject option after computationally expensive layers, implemented as a binary prediction for reject/keep (background/foreground for our detection task).
The goal of the Reject layer is to maintain high recall while culling as much of the batch as possible, so that we can avoid doing as much convolution in the next layer.
}\label{fig:ccnn}
\end{center}
\end{figure}

### 2014-12-15 conclusion.tex
8 pages
integrating changes from thesis

\section{Conclusion}\label{conclusion}

{[}Standard stuff{]}

\subsection{Future work}\label{future-work}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  ?
\end{itemize}

>>>>

\section{Conclusion}

Even the most recent state-of-the-art CNN-based detection methods are computationally expensive.
We first consider approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found early, based on inference from relatively lightweight features.
We show that basic strategies, such as simply reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can effectively prioritize regions.
Our main contribution is the Cascade CNN model, which adds a novel Reject layer between convolutional layers in the architecture.
C-CNN obtains an 8x speedup of the R-CNN detection method with only a 10\% degradation of state-of-the-art performance on PASCAL VOC detection.

### 2014-12-15 evaluation.tex
integrating changes from thesis

We evaluate on the standard object detection benchmark: the PASCAL VOC \cite{pascal-voc-2010}.
In all cases, the CNN region classifiers are trained on the PASCAL VOC 2007 trainval set.
The parameters of our methods are set by training or cross-validation on the VOC 2007 val set.
We evaluate on the VOC 2007 test set.

The scoring function for the quick-to-compute features is trained by a logistic regression classifier onto the max PASCAL overlap with any ground truth window on the validation dataset.
The classifier is optimized by stochastic gradient descent, and its regularization parameter is cross-validated.

The R-CNN software was used as available in June 2014.
\footnote{\url{https://github.com/rbgirshick/rcnn}}
That software relies on Selective Search \cite{Uijlings-IJCV-2013} region proposals.
Different images are proposed different numbers of regions.
\autoref{fig:roi_hist_and_gradient} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.
An additional parameter is the size of each batch of regions that goes through the CNN.
We set batch size to 100 regions, and observe that it takes on average 500 ms to process them with the CNN.
In all experiments, we use Ubuntu 12.04, Intel i5 3.2GHz CPU, and NVIDIA Tesla K40 GPU.

@@

\subsection{Experiments}
\begin{description}
  \item[Original] \hfill \\
  The original order of the Selective Search regions of interest.
  This order is influenced by the hierarchical segmentation of their method, and so has sequences of highly overlapping regions.

@@

  \item[Region Selection] \hfill \\
  The region statistics feature from \autoref{sec:region} is always used.
  Additionally, we consider the Pixel Gradient feature, with \emph{setup time} of the gradient forward-back propagation of 20 ms.

  \item[Cascaded CNN] \hfill \\
  The Cascaded CNN model, as described in \autoref{sec:ccnn}.
  The first experiment (C-CNN) takes batches of regions in a random order.
  The next two experiments also make use of the Region Selection methodology with the quick-to-compute feature.
\end{description}

\subsection{Analysis}
Since the time to process a full batch with a non-cascaded CNN is 500 ms, there are no results for non-cascaded baselines at 300 ms.
At this time, the Cascaded CNN without any region ordering is best.
A reason for why C-CNN with Region Selection is not as good at this point is that the region selection presents better region candidates, with fewer rejection opportunities, and thus has less coverage of the image.

At 600 ms, C-CNN method have had more than one batch go through, and the Region Selection is giving it a lead over the simple C-CNN.
Both method are better than the baseline non-cascaded methods for this entire duration.

\begin{figure}
\centering
\includegraphics[width=0.52\linewidth]{figures/roi_hist.pdf}
\hfill
\includegraphics[width=0.4\linewidth]{figures/gradient.pdf}
\caption{
(left) Distribution of number of regions per image.
(right) Example of the CNN gradient.
}\label{fig:roi_hist_and_gradient}
\end{figure}

>>>>

We evaluate on the standard object detection benchmark: the PASCAL VOC \cite{pascal-voc-2010}.
In all cases, the CNN region classifiers are trained on the PASCAL VOC 2007 trainval set.
The parameters of our methods are set by training or cross-validation on the VOC 2007 val set.
We evaluate on the VOC 2007 test set.
The result plots and details are shown in \autoref{fig:voc2007_results} and \autoref{tab:ccnn_results}.

The scoring function for the quick-to-compute features is trained by a logistic regression classifier onto the max PASCAL overlap with any ground truth window on the validation dataset.
The classifier is optimized by stochastic gradient descent, and its regularization parameter is cross-validated.
The R-CNN software was used as available in June 2014.
\footnote{\url{https://github.com/rbgirshick/rcnn}}
That software relies on Selective Search \cite{Uijlings-IJCV-2013} region proposals.
Different images are proposed different numbers of regions.
\autoref{fig:roi_hist} shows the distribution of number of regions on the validation set, with the parameters of the R-CNN.
An additional parameter is the size of each batch of regions that goes through the CNN.
We set batch size to 100 regions, and observe that it takes on average 500 ms to process them with the CNN.
In all experiments, we use Ubuntu 12.04, Intel i5 3.2GHz CPU, and NVIDIA Tesla K40 GPU.

@@

The experimental settings are
\begin{description}
  \item[Original] \hfill \\
  The original order of the Selective Search regions of interest.
  This order is influenced by the hierarchical segmentation of their method, and so has sequences of highly overlapping regions.

@@

  \item[Region Selection] \hfill \\
  The region statistics feature is always used.
  Additionally, we consider the Pixel Gradient feature, with \emph{setup time} of the gradient forward-back propagation of 20 ms.

  \item[Cascade CNN] \hfill \\
  The Cascade CNN model, as described in \autoref{sec:ccnn}.
  The first experiment (C-CNN) takes batches of regions in a random order.
  The next two experiments also make use of the Region Selection methodology with the quick-to-compute feature.
\end{description}

\subsection{Analysis}
Since the time to process a full batch with a non-cascaded CNN is 500 ms, there are no results for non-cascaded baselines at 300 ms.
At this time, the Cascade CNN without any region ordering is best.
A reason for why C-CNN with Region Selection is not as good at this point is that the region selection presents better region candidates, with fewer rejection opportunities, and thus has less coverage of the image.
At 600 ms, C-CNN method have had more than one batch go through, and the Region Selection is giving it a lead over the simple C-CNN.
Both method are better than the baseline non-cascaded methods for this entire duration.

### 2014-12-15 introduction.tex
integrating changes from thesis

The standard method for quickly applying a CNN to a large number of candidate regions is to restrict the regions to lie in a regular scale-space pyramid.
With this restriction, the CNN can efficiently compute features for all regions using convolution.
This approach was used in classical CNN-based detection systems as well as recent approaches such as OverFeat \cite{Sermanet-ICLR-2014}.
The recently proposed Regions with CNN features (R-CNN), in contrast, allows for more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows without sharing computation.
While R-CNN has leading performance on PASCAL and ImageNet detection as of the date of this writing, it is rather slow, at 10s per image on a GPU (following a separate region generation step).

In this paper, we investigate a novel approach for speeding up R-CNN and propose a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection datasets).
We bring the classic idea of the cascade to CNNs by inserting a \emph{reject} option between CNN layers.
When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.
We also consider a variety of strong baselines for speeding up R-CNN.

>>>>

The standard method for quickly applying a CNN to a large number of candidate regions is to restrict the regions to lie in a regular scale-space pyramid.
With this restriction, the CNN can efficiently compute features for all regions using convolution.
This approach was used in classical CNN-based detection systems as well as recent approaches such as OverFeat \cite{Sermanet-ICLR-2014}.
The recently proposed Regions with CNN features (R-CNN), in contrast, allows for more general region proposals guided by low-level segmentation cues (\cite{Uijlings-IJCV-2013}), but repeats the computation of convolutional features across numerous overlapping windows without sharing computation.

In this paper, we investigate a novel approach for speeding CNN-based detection methods and propose a general technique for accelerating CNNs applied to class imbalanced data (such as in object detection datasets).
We bring the classic idea of the cascade to CNNs by inserting a \emph{reject} option between CNN layers.
When the CNN processes batches of images, which is standard for many applications, the reject layers allows the CNN to ``thin'' the batch as it progresses through the network, thus saving processing time.

### 2014-12-15 method.tex
integrating changes from thesis

We first consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found early, based on inference from relatively lightweight features.
We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can effectively prioritize regions.

@@

\paragraph{Region statistics}\label{sec:region}
For the first source of information, we consider statistics about ROI location and overlap with other regions.
For each ROI, we compute: its normalized location, its scale($\sqrt{\text{width} \times \text{height}}$), aspect ratio ($\log \sqrt{\text{width} / \text{height}}$), and normalized counts of overlapping regions, at several PASCAL overlap thresholds (0, 0.2, 0.6).

This simple feature works suprisingly well for filtering regions to process first.
In concatenation, we also consider the \emph{pixel gradient}, back-propagated throgh a classification CNN applied to the whole image.
This feature corresponds to a kind of saliency map, giving an estimate of the importance of each pixel to the final classification of the image.

Our method follows \cite{Simonyan-ICLR-2014} to the best of our knowledge.
Images are resized to square and classified with an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN fine-tuned on the PASCAL VOC classification dataset with multi-label loss.
(Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.)
At test-time, the gradient at the top is with respect to the indicator function of the max-scoring class, and is back-propagated all the way to the pixels, where it is summed across channels.
A couple of example images are shown in \autoref{fig:roi_hist_and_gradient}.

We compute an integral image on this pixel gradient map, allowing near-instant computation of sums in arbitrary regions.
For each region to be evaluated, we compute the image-normalized gradient sum, sums for each of four corners, and ratio of in-region vs. out-of-region sums.

\subsection{Cascaded CNN}\label{sec:ccnn}

Most ROIs that are scored in R-CNN do not contain any object of interest.
It would be useful to quickly reject these regions, without expending the full amount of computation on them.

The Cascaded CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep processing the input with the next layer.
Each reject layer is implemented as a fully-connected layer following a linear rectification, trained with dropout using logistic loss on foreground/background labels.
We set the reject thresholds to maintain at last 80\% recall at each stage, using a large sample of regions from images in the validation set containing positive and negative examples in equal proportion.

>>>>

We first consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found early, based on inference from relatively lightweight features.

@@

\paragraph{Region statistics}\label{sec:region}
For the first source of information, we consider statistics about ROI location and overlap with other regions.
For each ROI, we compute: its normalized location, its scale ($\sqrt{\text{width} \times \text{height}}$), aspect ratio ($\log \sqrt{\text{width} / \text{height}}$), and normalized counts of overlapping regions, at several PASCAL overlap thresholds (0, 0.2, 0.6).
This simple feature works suprisingly well for filtering regions to process first.
In concatenation, we also consider the \emph{pixel gradient}, back-propagated throgh a classification CNN applied to the whole image.
This feature corresponds to a kind of saliency map, giving an estimate of the importance of each pixel to the final classification of the image.
Our method is independently developed, but agrees with the concurrently published work of \cite{Simonyan-ICLR-2014} quite closely.
Images are resized to square and classified with an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN fine-tuned on the PASCAL VOC classification dataset with multi-label loss.
(Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.)
At test-time, the gradient at the top is with respect to the indicator function of the max-scoring class, and is back-propagated all the way to the pixels, where it is summed across channels.
A couple of example images are shown in \autoref{fig:gradient_examples}.
We compute an integral image on this pixel gradient map, allowing near-instant computation of sums in arbitrary regions.
For each region to be evaluated, we compute the image-normalized gradient sum, sums for each of four corners, and ratio of in-region vs. out-of-region sums.

\begin{figure}[ht]
\centering
\begin{minipage}{.45\textwidth}
\centering
    \includegraphics[width=\linewidth]{figures/roi_hist.pdf}
    \caption{
    Distribution of number of regions per image.
    }\label{fig:roi_hist}
\end{minipage}\hfill%
\begin{minipage}{.45\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figures/gradient_backprop.pdf}
    \caption[Explanation of the gradient back-propagation quick feature.]{
    As a quick feature, we back-propagate the gradient from the top classification layer all the way to the input pixels.
    This induces a kind of saliency map on the image, which is useful signal for selecting image sub-regions to classify with the CNN.
    }\label{fig:gradient_examples}
\end{minipage}
\end{figure}

\subsection{Cascade CNN}\label{sec:ccnn}

Despite the intentions of the region-proposal mechanism \cite{Uijlings-IJCV-2013}, most ROIs that are scored in R-CNN do not contain any object of interest.
As in the classic cascade of \cite{Viola-IJCV-2004}, it would be useful to quickly reject these regions, without expending the full amount of computation on them.
The problem is that the deep neural network architecture is trained to always run all the way through.
We need to introduce a new primitive to enable early termination.

The Cascade CNN, shown in \autoref{fig:ccnn}, augments the CNN network with an ``Early Reject'' option: after some layers, the network decides whether to keep processing the input with the next layer.
Each reject layer is implemented as a fully-connected layer following a linear rectification, trained with dropout using logistic loss on foreground/background labels.
We first train an AlexNet-architecture network \cite{Krizhevsky-NIPS-2012} on the ImageNet classification dataset.
This network is augmented with the Reject layers, its loss replaced with a multi-label cross-entropy loss, and fine-tuning on the PASCAL VOC training set is performed until loss stop decreasing (roughly 50000 iterations).
In training, all instances pass through all Reject layers.
After training, we set the reject thresholds to maintain at last 80\% recall at each stage, using a large sample of regions from images in the validation set containing positive and negative examples in equal proportion.

### 2014-12-15 related_work.tex
integrating changes from thesis

The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{Deng-CVPR-2009} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-BMVC-2014,Simonyan-ICLR-2014,Erhan-CVPR-2014,Sermanet-ICLR-2014} .

>>>>

The recent success of deep convolutional neural networks (CNN) such as Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{Deng-CVPR-2009} has prompted many attempts to apply these computationally expensive methods to detection \cite{Girshick-CVPR-2014,Zou-BMVC-2014,Simonyan-ICLR-2014,Erhan-CVPR-2014,Sermanet-ICLR-2014,He-ECCV-2014} .

### 2014-12-15 voc2007_fig.tex
integrating changes from thesis

\begin{figure}[ht]
\centering
\begin{subfigure}[b]{0.52\linewidth}
    \includegraphics[width=\linewidth]{figures/_apvst_final.pdf}
    \caption{mAP vs. time allotted for detection}\label{fig:apvst}
\end{subfigure}\hfill
\begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{figures/_speedup_final_abs.pdf}
    \caption{mAP vs. speed-up factor}\label{fig:speedup}
\end{subfigure}
\caption{
Results on the PASCAL VOC 2007 dataset.
(a) On the left-hand mAP vs. Time plot, we can compare APs at a given allotted time point.
For example, at 1300 ms, random region selection gets about 0.42 mAP, while our best method (C-CNN with gradient-based region selection) obtains 0.50 mAP.
(b) On the right-hand speed-up plot, we can compare speed-ups at a given mAP point.
For example, we can see that we should obtain mAP of 0.40 at around 20x speedup with our method.
}\label{fig:voc2007_results}
\end{figure}

>>>>

\begin{figure}[ht]
\begin{subfigure}[b]{\linewidth}
    \centering
    \includegraphics[width=.75\linewidth]{figures/_apvst_final.pdf}
    \caption{
Plotting Mean AP vs. Time Allotted allows comparison performance at a given time budget.
For example, at 1300 ms, random region selection gets about 0.42 mAP, while our best method (C-CNN with gradient-based region selection) obtains 0.50 mAP.
}\label{fig:apvst}
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
    \centering
    \includegraphics[width=.75\linewidth]{figures/_speedup_final_abs.pdf}
    \caption{
Plotting mean AP vs. speed-up factor allows comparison of speed-ups at a given mAP point.
For example, we can see that we should obtain mAP of 0.40 at around 20x speedup with our method.
}\label{fig:speedup}
\end{subfigure}
\caption{
Results of the Cascade CNN and other Anytime methods on the PASCAL VOC 2007 dataset.
}\label{fig:voc2007_results}
\end{figure}
